---
title: "R Notebook"
output: 
  html_notebook:
    toc:true
---

```{r setup}
require(data.table)
require(ggplot2)
require(plotly)
require(DT)

N <- 5 # number of animals per group
n_trt <- 4 # number of treatment groups
```

# Data
#### 4 groups of mice: 1.Naive (healthy and untreated); 2. Vehicle (sick and treated with inactive part of the drug);  3. Treatment1 (sick and treated with one dose of the active drug suspended in vehicle); 3. Treatment2 (sick and treated with two dose of the active drug suspended in vehicle);
```{r data_sim}


dt1 <- data.table(Groups = rep(c("Naive",       
                               "Vehicle",
                              "Treatemt1", 
                               "Treatemt2"),
                               each = N),
                  ID = paste0("ID",
                              1:(N*n_trt))) 
datatable(dt1,
          rownames = FALSE)
```

# Add scores
####Naive group has low inflammation scores; the Vehicle-the highest; the Treatment1-somewhere in between; and Treatment 2-lower than Treatment 1 but higher than the Naive 
```{r add_vars}

dt1$Score[1:5] <- rnorm(N, mean = 0, sd=1) 
dt1$Score[6:10] <- rnorm(N, mean = 2, sd=1)
dt1$Score[11:15] <- rnorm(N, mean = 1, sd=1) 
dt1$Score[16:20] <- rnorm(N, mean = 0.5, sd=1) 
  
datatable(dt1)
```

```{r plot}
p1 <- ggplot(data = dt1,
             aes(x = Groups,
                 y = Score,
                 fill = ID)) +
  geom_point(shape = 21,
             size = 3,
             position = position_dodge(0.3))
print(p1)

ggplotly(p1)
```
