---
title: "R Notebook"
output: 
  html_notebook:
    toc:true
---

```{r setup}
require(data.table)
require(ggplot2)
require(plotly)
require(DT)

N <- 5 # number of animals per group
n_trt <- 5 # number of treatment groups
```

# Data
#### 4 groups of mice: 1.Naive (healthy and untreated); 2. Vehicle (sick and treated with inactive part of the drug);  3. TreatmentA (sick and treated with one active drug A suspended in vehicle); 4. TreatmentB (sick and treated with one active drug B suspended in vehicle); 5. TreatmentC (sick and treated with one active drug C suspended in vehicle)
```{r data_sim}
dt1 <- data.table(Groups = rep(c("Naive",
                                 "Vehicle",
                                 "TreatmentA",
                                 "TreatmentB",
                                 "TreatmentC"),
                               each = N),
                  ID = paste0("ID",
                              1:(N*n_trt)), Scores = rnorm(25,0,1))
datatable(dt1,
          rownames = FALSE)
```

# Add scores
#### Naïve group have low inflammation scores, the Vehicle  - the highest, and the TreatmentA  - somewhere in between, the TreatmentB - lower than the TreatmentA, but higher than the Naïve, the TreatmentC - lower than the TreatmentB, but higher than the Naïve.

```{r add_vars}
dt1$Score[1:5] <- rnorm(N, mean=0, sd=1)
dt1$Score[6:10] <- rnorm(N, mean=1, sd=1)
dt1$Score[11:15] <- rnorm(N, mean=0.7, sd=1)
dt1$Score[16:20] <- rnorm(N, mean=0.4, sd=1)
dt1$Score[21:25] <- rnorm(N,mean=0.2, sd=1)
datatable(dt1)
```

```{r plot}
p1 <- ggplot(data = dt1,
             aes(x = Groups,
                 y = Score,
                 fill = ID)) +
  geom_point(shape = 21,
             size = 3,
             position = position_dodge(0.3))
print(p1)

ggplotly(p1)
```

