---
title: "R Notebook"
output: 
  html_notebook:
    toc:true
---

```{r setup}
require(data.table)
require(ggplot2)
require(plotly)
require(DT)

N <- 10 # number of animals per group
n_trt <- 4 # number of treatment groups
```

# Data
### we creat 4 groups of mice: Naive (healthy and untreated), Vehicle (sick and treated with inactive part of the drug), Treatment A (sick and treated with active drug A ) and Treatment B (sick and treated with active drug B).
```{r data_sim}
dt1 <- data.table(Groups = rep(c("Naive",
                                 "Vehicle",
                                 "Treatment A",
                                 "Treatment B"),
                               each = N),
                  ID = paste0("ID",
                              1:(N*n_trt)),Scores = rnorm(40,0,1))
datatable(dt1,
          rownames = FALSE)
```

# Add scores
### Naive group have lowest inflammation score while the Vehicle have the highest inflammation score, group Treatment A and B are in between, but group Treatment A is higher than Treatment B.
```{r add_vars}
dt1$Score[1:10] <- rnorm(N,mean=2,sd=1)
dt1$Score[11:20] <- rnorm(N,mean=10,sd=1)
dt1$Score[21:30] <- rnorm(N,mean=5,sd=1)
dt1$Score[31:40] <- rnorm(N,mean=7,sd=1)
datatable(dt1)
```

```{r plot}
p1 <- ggplot(data = dt1,
             aes(x = Groups,
                 y = Score,
                 fill = ID)) +
  geom_point(shape = 21,
             size = 3,
             position = position_dodge(0.3))
print(p1)

ggplotly(p1)
```

