---
title: "R Notebook"
output: 
  html_notebook:
    toc:true
---

```{r setup, echo=FALSE, warning=FALSE, results='hide'}

require(data.table)
require(ggplot2)
require(plotly)
require(DT)
library(truncnorm)
library(drc)


N <- 10 # number of animals per group
n_trt <- 4 # number of treatment groups
```
# Data

There are four treatment groups: Naive, Vehicle, Dose1, Dose2<br>
Number of animals per group: 10<br>
Dataset of 40 observations is initialized with Group name and ID<br>

```{r data_sim, echo=FALSE, warning=FALSE, results='hide'}
dt1 <- data.table(Groups = rep(c("Naive",
                                 "Vehicle",
                                 "Dose1",
                                 "Dose2"),
                               each = N),
                  ID = paste0("ID",
                              1:(N*n_trt)))
datatable(dt1,
          rownames = FALSE)
```

# Add scores

(1) Dose response relationship analysis <br>
(2) Dataset table with Groups, ID and Score by different groups assigned. <br>

```{r add_vars, echo=FALSE, warning=FALSE}

dose <- 1:2
resp <- rtruncnorm(n = length(dose),a=0,b=1)

sort_resp <-c(min(resp),max(resp))

#sort_resp

m <- drm(sort_resp ~ dose, fct = LL.5())

summary(m)

plot(m)


dt1$Score <- ifelse(dt1$Groups=="Naive",rnorm(N, mean=1, sd=0.1), 
                        ifelse(dt1$Groups=="Vehicle",rnorm(N,mean=0, sd=0.1), 
                            ifelse(dt1$Groups=="Dose1",rnorm(N, mean=sort_resp[1], sd=0.1),
                            ifelse(dt1$Groups=="Dose2",rnorm(N, mean=sort_resp[2], sd=0.1),99))))
datatable(dt1)

```
# Plots analysis

(1) ggplot of Scores of each ID by groups <br>
(2) Advanced/interactive plot <br>
(3) Density score distribution comparison by groups

```{r plot, echo=FALSE, warning=FALSE}

p1 <- ggplot(data = dt1,
             aes(x = Groups,
                 y = Score,
                 fill = ID)) +
  geom_point(shape = 21,
             size = 3,
             position = position_dodge(0.3))
print(p1)


ggplotly(p1)

par(lwd=2) 
library(sm) 
attach(dt1)
Gp.f <- factor(Groups, levels= c("Vehicle","Dose1", "Dose2","Naive"),               
               labels = c("Vehicle","Dose1", "Dose2","Naive")) 
sm.density.compare(Score,Gp.f,xlab="Score")  
title(main="Score Distribution by Groups")
colfill<-c(2:(1+length(levels(Gp.f)))) 
legend("topleft",legend =c("Vehicle","Dose1", "Dose2","Naive"), fill=colfill )
detach(dt1) 
```

